On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-06-18 paper_lap/JCP_response1/response.tex

Remarks on content and readability

1) p. 2. The last sentence of the first paragraph mentions that the disadvantage of compression-based approaches to quadrature is cost in 3D. Given that these approaches have already been used in 3D problems, unlike the work in the current paper, I think that as a minimum there should be a couple of brief remarks somewhere about how the method here would extend and scale to 3D.

\qb

The discussion about the disadvantage of compression-based approaches in 3D has been removed and a discussion in the second last paragraph about generalizations to 3D has been added.

@@

\qa
2) p. 6. On a first reading, Theorem 6 is not easy to digest. Could you add a few comments to provide some intuition for this result, and also a comment on the connection of the result on an open wedge to the case of polygons? Do we expect the expansions to be exactly the same?

\qb

The notation in Theorem 6 has been cleaned up and a remark has been added afterward discussing the connection between the problem on the polygon and the problem on the wedge.

@@

\qa
3) p. 8. I think it is extremely important to explicitly discuss how large we expect K to be in section 4.1.1, especially how it relates to the accuracy a user might desire. I realize the relevant information is likely in [14], but it is of sufficient importance to the current work to make this clear by either stating a result or computational experience.

The value of K used in our experiments has been stated explicitly.

@@

The value of K used in our experiments has been stated explicitly.

\qa
4) p. 11. The theory as developed considers only the exterior Neumann problem. I?m guessing a similar duality relationship holds with the interior Neumann problem and the exterior Dirichlet problem, and the procedure carries over straightforwardly (indeed, you consider an interior Neumann problem in the numerical results). For the sake of completeness, could you add a brief remark on whether or not the procedure is exactly the same for the interior Neumann problem, and state if there are any special considerations that are different from the exterior Neumann case?

We thank the referee for pointing this out. A comment has been added discussing the interior Neumann problem.

@@

We thank the referee for pointing this out. A comment has been added discussing the interior Neumann problem.

\qa
5) p. 13. I find the choice of notation in Theorem 8 to be very poor. In particular $A_{0}$ and $f_{0}$ are
used right above in (56) to denote the local problem after the corner has been refined ($A_{0}$ is of size
$P + 2M \times P + 2M$). Then in the statement of the theorem, these variables are used to denote the
analogous variables on just the corner panel of the unrefined problem ($A_{0}$ is of size $P \times P$ ), and then
in the proof of the result these variables are used to refer to the original corner panel as well as the
adjacent panels ($A_{0}$ is of size $P + 2M \times P + 2M$ ). Also, I am not sure why $f_{0}$ is not underlined, since it is a vector. Could you please fix this notation?

The theorem has been eliminated in favor of a remark, and the corresponding notation has been cleaned up.

@@

There are these other issues I?m having with it:
(a) On your assumptions about the discretization, 1 and 3 have an easy-to-understand interpretation. It's unclear to me what 2 is really assuming about the discretization, given that it seems to mostly to be introducing notation. Of course, I can imagine conditions where $\rho_{0}$ is less than the width of some panels, but is there some deeper restriction?
(b) Your assumption that $\rho_{0}>1$ and your later statement that the rate at which a polynomial interpolant will converge is $C \rho_{0}^{M}$ is a bit awkward, since these choices are specific for a function
on an interval of length 2.
(c) The second paragraph on p. 22 is very unclear to me. I don?t even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as $\gamma([s1,s2])$, or what is really even meant by ?segment? here. Furthermore, it is mentioned that k(s, t) when considered as a function of $t \in \mathbb{C}$ has a singularity at $\gamma(s)$. Given the current setup wouldn't the singularity be at s? I would recommend rewriting this entire paragraph to be more transparent.

\qb
Thank you for bringing this to our notice. The section as written was confusing and we have rewritten the section completely to address all of the concerns above and feel that the readability now is significantly improved. We have eliminated the assumptions on the geometry completely as it can be confusing and rather reduced it to an error estimate of a solution to a Dirichlet problem using the same grid. The purpose of our approach is to show that a good Dirichlet discretization of the corner problem can be reutilized to obtain a discretization of the Neumann problem.
\qa
Small fixes and typos:

\qb
We thank the referee for pointing out these typos and small fixes!

### 2020-07-15 paper_lap/JCP_response1/response.tex

\address{Jeremy Hoskins (Yale University)\\
jeremy.hoskins@yale.edu\\
\vspace{.02in}\\
Manas Rachh (Flatiron Institute)\\
mrachh@flatironinstitute.org}

\begin{letter}{Editorial Office\\
Journal of Computational Physics - X}

\opening{Dear Editor:}

The following document contains a response to the comments made by the
reviewers after reading our manuscript \emph{On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains}.

Below are the reviewers' reports indented and in italics, interlaced with
our responses.

\qa
Reviewer \#1:
This manuscript extends a recent line of work on handling the singularities in the density of the standard boundary integral equation formulation of Laplace's equation that arise at the corners of polygonal domains, through the use of specialized, high-order quadratures, which are computed using analytic expansions of the density. Previous work in this direction has difficulties directly applying this strategy to Neumann problems, since the singularities are significantly worse here than in the Dirichlet case. The current work makes the incredibly interesting observation that one can instead use the adjoint of a discretization to the Dirichlet problem to obtain a solution that is accurate in a weak sense. Furthermore, pointwise accuracy in a region arbitrarily close to a corner can be obtained through a novel local refinement process. The relevant theory for justifying both that this approach yields a density that can be accurately interpolated away from the corners and that the refinement process can be done in a completely local manner is developed. Furthermore, the approach is illustrated through exceptionally thorough and impressive numerical results.

@@

\qa
3) p. 8. I think it is extremely important to explicitly discuss how large we expect K to be in section 4.1.1, especially how it relates to the accuracy a user might desire. I realize the relevant information is likely in [14], but it is of sufficient importance to the current work to make this clear by either stating a result or computational experience.

\qb

The value of K used in our experiments has been stated explicitly.

\qa
4) p. 11. The theory as developed considers only the exterior Neumann problem. I'm guessing a similar duality relationship holds with the interior Neumann problem and the exterior Dirichlet problem, and the procedure carries over straightforwardly (indeed, you consider an interior Neumann problem in the numerical results). For the sake of completeness, could you add a brief remark on whether or not the procedure is exactly the same for the interior Neumann problem, and state if there are any special considerations that are different from the exterior Neumann case?

@@

\qb
We use a version of GMRES which does not suffer from stagnation at low thresholds and an FMM whose tolerance was set to $5 \times 10^{-16}$. The number of iterations do not reduce drastically if we increase the iteration count. We attach here a plot of the relative residual as a function of iteration number. 
\begin{center}
\includegraphics[width=0.7\linewidth]{lap-iter-count-wheel.pdf}
\end{center}

Our boundary data has randomly generated charge strengths and sources. For a new run, the original discretization requires $106$ iterations for the Neumann problem. The iteration count for the corresponding adjoint Dirichlet problem is $83$, and iteration count on doubling the number of points in our existing discretization is $106$.

\qa
8) 
p. 21-22. I find the content of Appendix B difficult to understand for a number of reasons. The motivation for such a result is clear, but I'm not sure I totally understand the conclusion. In particular, you want to show that using the adjoint discretization one can interpolate the density on a panel far from the corner. That makes sense. Your approach to showing this is to use the relation (B.1) to find another equivalent integral equation, which you then show can be solved using existing information accurately.
Is the claim that to actually interpolate the density on such a panel, one would need to solve another Dirichlet problem, and it does NOT suffice to just interpolate the value of $\sigma$ obtained on the GL nodes when solving the original problem? Please clarify this point.

There are these other issues I'm having with it:
(a) On your assumptions about the discretization, 1 and 3 have an easy-to-understand interpretation. It's unclear to me what 2 is really assuming about the discretization, given that it seems to mostly to be introducing notation. Of course, I can imagine conditions where $\rho_{0}$ is less than the width of some panels, but is there some deeper restriction?
(b) Your assumption that $\rho_{0}>1$ and your later statement that the rate at which a polynomial interpolant will converge is $C \rho_{0}^{M}$ is a bit awkward, since these choices are specific for a function
on an interval of length 2.
(c) The second paragraph on p. 22 is very unclear to me. I don't even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as $\gamma([s1,s2])$, or what is really even meant by segment here. Furthermore, it is mentioned that k(s, t) when considered as a function of $t \in \mathbb{C}$ has a singularity at $\gamma(s)$. Given the current setup wouldn't the singularity be at s? I would recommend rewriting this entire paragraph to be more transparent.

@@

\qb
Thank you for bringing this to our notice. The section as written was confusing and we have rewritten the section completely to address all of the concerns above and feel that the readability now is significantly improved. We have eliminated the assumptions on the geometry completely as it can be confusing and rather reduced it to an error estimate of a solution to a Dirichlet problem using the same grid. The purpose of our approach is to show that a good Dirichlet discretization of the corner problem can be reutilized to obtain a discretization of the Neumann problem.
\qa
Small fixes and typos:

\qb
We thank the referee for pointing out these typos and small fixes!

\qa
Reviewer \#4:
This article is not suitable for JCP. Most of it is Theorem, Lemma, Proposition, Remark. Journal of Computational Physics focuses on computational aspects of physical problems and contributions in mathematical and numerical modeling, rather than numerical analysis. This paper should be submitted to SIAM NUM ANALYS., or IMA J. NUM. ANAL., or Numerische Mathematik.

\qb
The solution of Laplace's equation in complicated domains is a classical problem in computational physics and has many applications such as electrostatics, fluid flow, diffusion, and magnetohydrodynamics to name a few.  We have significantly reduced the use of theorems and definitions to summarize classical results and standard definitions.  Here are a few other examples of papers in JCP which we believe are written in a similar style.

\begin{enumerate}
\item G. Widmer, R. Hiptmair, C. Schwab, Sparse adaptive finite elements for radiative transfer, Journal of Computational Physics 227 (2008) 6071-6105. 
\item K. Serkh, V. Rokhlin, On the solution of elliptic partial differential equations on regions with corners, Journal of Computational Physics 305 (2016) 150-171.
\item C. Jerez-Hanckes, C. Peres-Arancibia, C. Turc, Multitrace/single trace fomulations and domain decomposition methods for the solution of Helmholtz transmission problems for bounded composite scatterers, Journal of Computational Physics 350 (2017) 343-360. 
\end{enumerate}

### 2020-07-15 paper_lap/JCP_response1/01intro.tex
updating response and manuscript

 Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{serkhacha,serkh2016solution}. Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e. an amount which is comparable to the number required for smooth portions of the boundary). This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{hoskins2019numerical}.

>>>>

 Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{serkhacha,serkh2016solution}. Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e. an amount which is comparable to the number required for smooth portions of the boundary). This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains~\cite{hoskins2019numerical}.

### 2020-07-15 paper_lap/JCP_response1/02mprelim.tex
adding response
updating response and manuscript

\section{Mathematical preliminaries \label{sec:mprelim}}
\subsection{Boundary value problems}
Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and outward-pointing 
unit normal $\bnu$, as well as a function 
$f: \Gamma \to \mathbb{R},$ we consider 
the following four boundary value problems.

\begin{enumerate}
\item The interior Dirichlet problem for Laplace's equation:
\begin{align}\label{eqn:BVPIDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
u(\bx) &= f(\bx), \hspace{0.43 cm} \bx \in \Gamma.
\end{align}

\item The exterior Dirichlet problem for Laplace's equation:
\begin{align}\label{eqn:BVPEDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
u(\bx) &= f(\bx), \hspace{0.43 cm}\bx \in \Gamma, \\
u(\bx) &= O(1) , \hspace{0.4cm} |\bx| \to \infty.
\end{align}

\item The interior Neumann problem for Laplace's equation:
\begin{align}\label{eqn:BVPINL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.45 cm} \bx \in \Gamma,\\
\int_\Gamma f(\bx) {\rm d}S_{\bx} &= 0.
\end{align}

\item The exterior Neumann problem for Laplace's equation:
\begin{align}\label{eqn:BVPEDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.43 cm} \bx \in \Gamma, \\
&\hspace{-2 cm}\left|u(\bx) + \left(\frac{1}{2\pi} \int_\Gamma f(\bx) {\rm d}S_{\bx}\right) \log{|\bx|}\right| \to 0 , \hspace{0.4cm} |\bx| \to \infty.
\end{align}

@@

\begin{remark}
The existence and uniqueness of the solutions to the above equations is a well-known result (see \cite{} for example). 
\end{remark}

>>>>

\section{Mathematical preliminaries \label{sec:mprelim}}
\subsection{Boundary value problems}
Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and outward-pointing 
unit normal $\bnu$, as well as a function 
$f: \Gamma \to \mathbb{R},$ we consider 
the following four boundary value problems for Laplace's equation.

\begin{enumerate}
\item The interior Dirichlet problem:
\begin{align}\label{eqn:BVPIDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
u(\bx) &= f(\bx), \hspace{0.43 cm} \bx \in \Gamma.
\end{align}

\item The exterior Dirichlet problem:
\begin{align}\label{eqn:BVPEDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
u(\bx) &= f(\bx), \hspace{0.43 cm}\bx \in \Gamma, \\
u(\bx) &= O(1) , \hspace{0.4cm} |\bx| \to \infty.
\end{align}

\item The interior Neumann problem:
\begin{align}\label{eqn:BVPINL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.45 cm} \bx \in \Gamma,\\
\int_\Gamma f(\bx) {\rm d}S_{\bx} &= 0.
\end{align}

\item The exterior Neumann problem:
\begin{align}\label{eqn:BVPEDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.43 cm} \bx \in \Gamma, \\
&\hspace{-2 cm}\left|u(\bx) + \left(\frac{1}{2\pi} \int_\Gamma f(\bx) {\rm d}S_{\bx}\right) \log{|\bx|}\right| \to 0 , \hspace{0.4cm} |\bx| \to \infty.
\end{align}

@@

\begin{remark}
The existence and uniqueness of the solutions to the above equations is a well-known result (see \cite{kress1989linear} for example). 
\end{remark}

### 2020-07-15 paper_lap/JCP_response1/03bvp.tex
updating response and manuscript

 \section{Boundary integral equations \label{sec:bvp}}
A classical technique for solving the four Laplace boundary value problems given above is to reduce them to boundary integral equations. Before describing this procedure we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}\label{def_layerpots}
Given a function $\sigma:\Gamma \to \mathbb{R}$, the single-layer potential is defined by
\beqn
\cS[\sigma](\by) =  \int_{\Gamma} G (\bx,\by)\sigma(\bx) {\rm d}S_{\bx} \, ,
\eeqn
where
\beqn
G(\bx,\by) = -\frac{1}{2\pi} \log{|\bx-\by|}.
\eeqn
Similarly, the double-layer potential is defined via the formula
\beqn
\cD[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by) \sigma(\bx) {\rm d}S_{\bx}.
\eeqn
\end{definition}
In the following we will often refer to the function $\sigma$ as the {\it density} which generates the corresponding potential.
\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K(\bx,\by)$ by
\begin{equation}
K(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by),
\end{equation}
where $\bnu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
work instead with a parametrization of $K.$ In particular, if $\gamma :[0,L] \to \Gamma$ is a counterclockwise 
arclength parametrization of $\Gamma,$ 
we denote by $k:[0,L]\times [0,L] \to \mathbb{R}$ the function defined by
\begin{align}
k(s,t) = K(\gamma(s),\gamma(t)).
\end{align}
\upd{By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
\end{definition}

@@

Next we define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}\label{def_singder}
Let $\cS$ be the single-layer potential operator and $\bnu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\bx_0 \in \Gamma,$
\begin{align}
\bnu(\bx_0)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)).
\end{align}
\end{definition}

The following proposition relates the normal derivative of the single-layer operator to the double-layer operator. Its proof follows directly from Definitions \ref{def_layerpots} and \ref{def_singder}.
\begin{proposition}
Let $\cS,\cD:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above. Let $\bnu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition. Then $\bnu \cdot \nabla \cS= \cD^{T}$ where $T$ denotes the adjoint operator with respect to the inner product
\beqn
\langle f,g \rangle = \int_{0}^{L} f(\gamma(t)) g(\gamma(t)) {\rm d}t\,,
\eeqn
where $\gamma:[0,L] \to \Gamma$ is a counterclockwise arclength parametrization of $\Gamma.$ 
In particular, for all $\rho,\sigma \in L^2(\Gamma),$
\begin{align}
\cD[\sigma](\gamma(t)) = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
\end{align}
and
\begin{align}
\bnu(\gamma(t))\cdot \nabla\cS[\rho](\gamma(t)) = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
\end{align}
\end{proposition}

\subsection{Reduction of boundary value problems}
In this section we describe the conversion of the Laplace boundary value problems (interior Dirichlet, exterior  Dirichlet, interior Neumann, and exterior Neumann) to second-kind integral equations.

\begin{theorem} [Interior Dirichlet problem for Laplace's equation]
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L]),$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
\begin{align}
f(s)= - \frac{\sigma(s)}{2}+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
for all $s \in [0,L).$ Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem} [Exterior Dirichlet problem for Laplace's equation]
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which
satisfies
\begin{align}
f(s)=  \frac{\sigma(s)}{2}+ \int_0^L (k(t,s) + 1)\,\sigma(t)\,{\rm d}t,
\end{align}\label{bie_extd}
for all $s \in [0,L].$ 
Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem}[Interior Neumann problem for Laplace's equation]
For every  $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ such that $\int_{0}^{L} f(t)\,{\rm d}t = 0,$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
\begin{align}
f(s)=  \frac{\sigma(s)}{2}+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
\label{bie_intn}
\end{align}
for all $s \in [0,L).$ Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}[Exterior Neumann problem for Laplace's equation]
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
\begin{align}
f(s)=  \frac{\sigma(s)}{2}+ \int_0^L k(s,t) \,\sigma(t)\,{\rm d}t,
\label{bie_extn}
\end{align}
for all $s \in [0,L).$ Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

>>>>

 \section{Boundary integral equations \label{sec:bvp}}
A classical technique for solving the four Laplace boundary value problems given above is to reduce them to boundary integral equations. Before describing this procedure we first define the single and double layer potential operators and summarize their relevant properties.
\upd{
 \subsection{Layer potentials}
Given a function $\sigma:\Gamma \to \mathbb{R}$, the single-layer potential is defined by
\beqn
\cS[\sigma](\by) =  \int_{\Gamma} G (\bx,\by)\sigma(\bx) {\rm d}S_{\bx} \, ,
\eeqn
where
\beqn
G(\bx,\by) = -\frac{1}{2\pi} \log{|\bx-\by|}.
\eeqn
Similarly, the double-layer potential is defined via the formula
\beqn
\cD[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by) \sigma(\bx) {\rm d}S_{\bx}.
\eeqn
In the following we will often refer to the function $\sigma$ as the {\it density} which generates the corresponding potential.

For $\bx \in \Gamma$ we define the kernel $K(\bx,\by)$ by
\begin{equation}
K(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by),
\end{equation}
where $\bnu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
work instead with a parametrization of $K.$ In particular, if $\gamma :[0,L] \to \Gamma$ is a counterclockwise 
arclength parametrization of $\Gamma,$ 
we denote by $k:[0,L]\times [0,L] \to \mathbb{R}$ the function defined by
\begin{align}
\label{eq:def_kerst}
k(s,t) = K(\gamma(s),\gamma(t)).
\end{align}
By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}

@@

Next we define the following operator which arises in the study of Neumann boundary value problems.
Let $\cS$ be the single-layer potential operator and $\bnu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\bx_0 \in \Gamma,$
\begin{align}
\bnu(\bx_0)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)).
\end{align}

\upd{
It is well known that $\bnu \cdot \nabla \cS = \cD^{T}$ where $^T$ denotes the adjoint with respect to
the inner product, 
\beqn
\langle f,g \rangle = \int_{0}^{L} f(\gamma(t)) g(\gamma(t)) {\rm d}t\,,
\eeqn
and $\gamma:[0,L] \to \Gamma$ is a counterclockwise arclength parametrization of $\Gamma.$  
In particular, for all $\rho,\sigma \in L^2(\Gamma),$
\begin{align}
\cD[\sigma](\gamma(t)) = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
\end{align}
and
\begin{align}
\bnu(\gamma(t))\cdot \nabla\cS[\rho](\gamma(t)) = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s \,
\end{align}
where $k(s,t)$ is defined in~\cref{eq:def_kerst}.

\subsection{Reduction of boundary value problems}
In this section we describe the conversion of the Laplace boundary value problems (interior Dirichlet, exterior  Dirichlet, interior Neumann, and exterior Neumann) to second-kind integral equations. \upd{These results are classical and we present them below for completeness (see~\cite{kress1989linear}, for example).}

\begin{enumerate}
\item Interior Dirichlet problem: \\ 
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L]),$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
\begin{align}
f(s)= - \frac{\sigma(s)}{2}+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
for all $s \in [0,L).$ Moreover, the solution to the interior Dirichlet problem with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$

\item Exterior Dirichlet problem:\\ 
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which
satisfies
\begin{align}
f(s)=  \frac{\sigma(s)}{2}+ \int_0^L (k(t,s) + 1)\,\sigma(t)\,{\rm d}t,
\end{align}\label{bie_extd}
for all $s \in [0,L].$ 
Moreover, the solution to the exterior Dirichlet problem with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$

\item Interior Neumann problem:\\ 
For every  $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ such that $\int_{0}^{L} f(t)\,{\rm d}t = 0,$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
\begin{align}
f(s)=  \frac{\sigma(s)}{2}+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
\label{bie_intn}
\end{align}
for all $s \in [0,L).$ Moreover, a solution to the interior Neumann problem with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$

\item Exterior Neumann problem:\\
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
\begin{align}
f(s)=  \frac{\sigma(s)}{2}+ \int_0^L k(s,t) \,\sigma(t)\,{\rm d}t,
\label{bie_extn}
\end{align}
for all $s \in [0,L).$ Moreover, the solution to the exterior Neumann problem with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \mathbb{R}^{2} \setminus \Omega.$
\end{enumerate}
}

### 2020-07-15 paper_lap/JCP_response1/04nprelim.tex
updating response and manuscript

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,\upd{x_i}) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
\begin{remark}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^1 k(t,-x_i) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_i$ was one of the original discretization nodes generated on the interval $[0,1].$
\end{remark}
\begin{remark}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,\upd{x_i}) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{\upd{i,j}} \tilde{\phi}_{m}(\upd{x_j}) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark}

@@

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range $(-1/2,0)$) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead, a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.

@@

\upd{For ease of exposition, here we describe the exterior Neumann problem though an identical procedure can be used for the interior Neumann problem. In the latter case it is well-known that the naive boundary integral equation formulation has a one-dimensional nullspace (corresponding to the fact that solutions to the corresponding PDE are unique only up to a constant). Using standard techniques (see \cite{} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}

>>>>

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When \upd{$x_i$} corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,\upd{x_i}) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
\begin{remark}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^1 k(t,-x_i) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_i$ was one of the original discretization nodes generated on the interval $[0,1].$
\end{remark}
\begin{remark}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,\upd{x_i}) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{\upd{i,j}} \tilde{\phi}_{m}(\upd{x_j}) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark}

@@

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range \upd{$(-1/2,1/2)$} makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead, a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.

@@

\upd{For ease of exposition, here we describe the exterior Neumann problem though an identical procedure can be used for the interior Neumann problem. In the latter case it is well-known that the naive boundary integral equation formulation has a one-dimensional nullspace (corresponding to the fact that solutions to the corresponding PDE are unique only up to a constant). Using standard techniques (see \cite{sifuentes2014randomized} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}
